---
title: "Glycans visualize data"
author: "Reto Gerber"
date: "`r Sys.Date()`"
output: 
  html_document:
    self_contained: TRUE
    code_folding: "hide"
    toc: true
    toc_float: true
    toc_collapsed: true
toc_depth: 3
number_sections: true
theme: lumen
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 144, dev = "png")
all_times <- list() # store the time for each chunk
knitr::knit_hooks$set(time_it = local({
  now <- NULL
  function(before, options) {
    if (before) {
      now <<- Sys.time()
    } else {
      res <- difftime(Sys.time(), now)
      all_times[[options$label]] <<- round(lubridate::as.duration(res))
    }
  }
}))
knitr::opts_chunk$set(time_it = TRUE)
```

```{r, warning=FALSE, message=FALSE}
suppressPackageStartupMessages(suppressWarnings({
  library(tidyverse)
  library(SpatialExperiment)
}))
RhpcBLASctl::blas_set_num_threads(10)
output_dir <- "./output"
```
# Read data

```{r read_and_combine}
imcims_df <- data.table::fread(file.path(output_dir, "imc_to_ims_workflow_imcims_full_combined.csv"), na.strings = "")
imcims_df <- imcims_df[imcims_df$in_IMC,]
```



# Prepare

```{r}
is_mz_col <- stringr::str_detect(colnames(imcims_df), "[:digit:]{4}")
mzcol_names <- colnames(imcims_df)[is_mz_col]
mzcol <- as.numeric(mzcol_names)
mzval <- mzcol_names[1]
```

```{r unique_ims_pixels}
imcims_df_px <- imcims_df %>%
  dplyr::select(!!dplyr::all_of(mzcol_names), TMA_type, sample_id, ims_idx, Identifier, maldi_step_size, to_keep_reg) %>%
  data.table::as.data.table() %>%
  unique() %>%
  as.data.frame()
is_mz_col_px <- stringr::str_detect(colnames(imcims_df_px), "[:digit:]{4}")
```




# Distribution of total sum of intensities (per pixel)


```{r}
data.frame(
  total = apply(imcims_df_px[, is_mz_col_px],1,function(x) sum(na.omit(x))),
  TMA_type = imcims_df_px$TMA_type,
  maldi_step_size = as.character(imcims_df_px$maldi_step_size),
  Identifier = imcims_df_px$Identifier,
  sample_id = imcims_df_px$sample_id,
  to_keep_reg = imcims_df_px$to_keep_reg
) %>%
  ggplot() +
  geom_density(aes(total, color = to_keep_reg, group = sample_id), linewidth = 0.3, alpha = 0.1) +
  geom_density(aes(total), linewidth = 1, color = "black") +
  theme_bw() +
  facet_wrap(~TMA_type) +
  scale_color_viridis_d()
```

# Distribution of cell overlap

the cell overlap is the proportion of area a cell overlaps with a IMS pixel. I.e. a value of 1 means the cell is completely inside a IMS pixel.

```{r,fig.width=10}
mc <- imcims_df %>%
  dplyr::group_by(cell_idx, sample_id) %>%
  dplyr::tally() %>%
  dplyr::filter(n > 1) %>%
  dplyr::pull(cell_idx)

imcims_df %>%
  dplyr::filter(cell_idx %in% mc) %>%
  ggplot() +
  geom_density(aes(overlap, color = to_keep_reg, group = sample_id), linewidth = 0.15, alpha = 0.1) +
  geom_density(aes(overlap), linewidth = 1, color = "black") +
  theme_bw() +
  facet_wrap(~TMA_type) +
  scale_color_viridis_d()
```


# IMS stats

## Number of IMS pixels:

```{r}
imcims_df_px %>%
  dplyr::group_by(TMA_type) %>%
  dplyr::select(TMA_type, ims_idx) %>%
  unique() %>%
  dplyr::tally() %>%
  as.data.frame()
```

## Number of cells:

```{r}
imcims_df %>%
  dplyr::group_by(TMA_type) %>%
  dplyr::select(TMA_type, ims_idx, cell_idx) %>%
  unique() %>%
  dplyr::tally() %>%
  as.data.frame()
```

Distribution of number of cells.

```{r}
imcims_df %>%
  dplyr::group_by(TMA_type, ims_idx,sample_id) %>%
  dplyr::select(TMA_type, ims_idx, cell_idx,sample_id) %>%
  dplyr::summarise(ncells = length(cell_idx[!is.na(cell_idx)])) %>%
  ggplot() +
  geom_histogram(aes(x = ncells, fill = TMA_type), position = "dodge", binwidth = 0.5)
```

summary

```{r}
ncells_per_ims <- imcims_df %>%
  dplyr::group_by(TMA_type, ims_idx,sample_id) %>%
  dplyr::select(TMA_type, ims_idx, cell_idx,sample_id) %>%
  dplyr::summarise(ncells = length(cell_idx[!is.na(cell_idx)])) %>%
  dplyr::group_by(TMA_type) %>%
  dplyr::summarise(
    sd_ncells = sd(ncells),
    mean_ncells = mean(ncells),
    median_ncells = median(ncells)
  ) %>%
  as.data.frame() %>%
  dplyr::arrange(TMA_type)
ncells_per_ims
```

# Pixel level statistics


```{r}
imcims_df_full <- imcims_df %>%
  dplyr::mutate(cell_area=ifelse(is.na(cell_area),0,cell_area)) %>%
  dplyr::mutate(overlap=ifelse(is.na(overlap),0,overlap)) %>%
  dplyr::mutate(
    maldi_area_filled = overlap * cell_area,
    prop_maldi_area_filled = maldi_area_filled / (maldi_pixel_size**2)
  ) %>%
  dplyr::group_by(ims_idx, sample_id) %>%
  dplyr::mutate(total_cell_area_in_maldi = sum(maldi_area_filled)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(cell_idx, sample_id) %>%
  dplyr::mutate(
    overlap_weight = maldi_area_filled / total_cell_area_in_maldi,
    cell_scaling_factor = cell_area / total_cell_area_in_maldi
  ) %>%
  dplyr::mutate(overlap_weight=ifelse(is.nan(overlap_weight),1,overlap_weight)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(celltype) %>%
  dplyr::mutate(ncells_celltype = dplyr::n()) %>%
  dplyr::ungroup() %>%
  # remove celltypes with too few cells
  dplyr::filter(ncells_celltype > 2) 
```

save the data

```{r save_rds}
data.table::fwrite(imcims_df_full,file.path(output_dir, "imc_to_ims_workflow_imcims_combined_full.csv"))
```


```{r, fig.width=10,fig.height=6}
imcims_df_full_px <- imcims_df_full %>%
  dplyr::select(ims_idx, TMA_type, sample_id, maldi_area_filled, prop_maldi_area_filled) %>%
  dplyr::group_by(ims_idx, TMA_type, sample_id) %>%
  dplyr::summarise(
    maldi_area_filled = sum(maldi_area_filled),
    prop_maldi_area_filled = sum(prop_maldi_area_filled)
  ) %>%
  unique()

imcims_df_full_px %>%
  tidyr::pivot_longer(cols = c("maldi_area_filled", "prop_maldi_area_filled")) %>%
  ggplot() +
  geom_density(aes(group = sample_id, x = value, color = TMA_type), linewidth = 0.15, alpha = 0.1) +
  geom_density(aes(group = TMA_type, x = value, color = TMA_type), linewidth = 1) +
  facet_wrap(~name, scales = "free")
```


# Session Info

```{r sessioninfo}
cat(paste0("Total Run time: ", purrr::reduce(all_times, `+`)))

print("Run times of chunks:")
print(all_times)

sessionInfo()
```
