---
title: "Glycans test assocations"
author: "Reto Gerber"
date: "`r Sys.Date()`"
output: 
  html_document:
    self_contained: TRUE
    code_folding: "hide"
    toc: true
    toc_float: true
    toc_collapsed: true
toc_depth: 3
number_sections: true
theme: lumen
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 144, dev = "png")
all_times <- list() # store the time for each chunk
knitr::knit_hooks$set(time_it = local({
  now <- NULL
  function(before, options) {
    if (before) {
      now <<- Sys.time()
    } else {
      res <- difftime(Sys.time(), now)
      all_times[[options$label]] <<- round(lubridate::as.duration(res))
    }
  }
}))
knitr::opts_chunk$set(time_it = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
# suppressPackageStartupMessages(suppressWarnings({
# library(tidyverse)
# }))
n_workers <- 28
RhpcBLASctl::blas_set_num_threads(n_workers)
analysis_dir <- "."
output_dir <- "./output"
source(file.path(analysis_dir, "imcims_model.R"))
```



# Prepare Data

```{r load_data}
imcims_df_full <- data.table::fread(file.path(output_dir, "imc_to_ims_workflow_imcims_combined_full.csv"))
imcims_df_full$celltype[imcims_df_full$celltype==""] <- NA
```

```{r}
is_mz_col <- stringr::str_detect(colnames(imcims_df_full), "[:digit:]{4}")
mzcol_names <- colnames(imcims_df_full)[is_mz_col]
mzcol <- as.numeric(mzcol_names)
```


```{r}
celltypes <- unique(imcims_df_full$celltype)
celltypes <- celltypes[!is.na(celltypes)]
celltypes <- sort(celltypes)
```




## to wide

```{r to_wide}
imcims_df_full <- imcims_df_full |>
  dplyr::group_by(sample_id, ims_idx) |>
  dplyr::mutate(n_cells_per_pixel = length(cell_idx[!is.na(cell_idx)])) |>
  dplyr::ungroup()
imcims_wide <- to_wide(
  imcims_df_full,
  column_names = list(
    sample_name = "sample_id",
    celltype = "celltype",
    value = "prop_maldi_area_filled",
    imsid = "ims_idx",
    coords = c("ims_x", "ims_y"),
    responses = mzcol_names,
    covariates = c("TMA_type", "Identifier","sample_type","to_keep_reg")
  )
)

if ("NA" %in% colnames(imcims_wide)) {
  imcims_wide[["NA"]] <- NULL
}
```

```{r}
imcims_wide <- data.table::as.data.table(imcims_wide)
imcims_wide$ims_idx <- as.character(imcims_wide$ims_idx)
data.table::setkey(imcims_wide, sample_id)
data.table::setindex(imcims_wide, sample_id)
data.table::setindex(imcims_wide, ims_idx)
data.table::setindex(imcims_wide, sample_id, ims_idx)
```




### neighborhoods


```{r create_neighborhood_lists}
xl <- split(imcims_wide$ims_x, imcims_wide$sample_id)
yl <- split(imcims_wide$ims_y, imcims_wide$sample_id)
rnl <- split(paste0(imcims_wide$sample_id, ".", imcims_wide$ims_idx), imcims_wide$sample_id)
dat_ls <- lapply(seq_along(xl), \(k){
  list(
    x = xl[[k]],
    y = yl[[k]],
    rownam = rnl[[k]]
  )
})
names(dat_ls) <- names(xl)
wmls_ls <- all_neighborhoods(dat_ls, max_dist = 1)
names(wmls_ls) <- names(xl)
```







# Run models



## First level: Spatial lag model

For one specific glycan fit the following model:
$$
y=ρWy+Xβ+ε
$$
with $y$ the response (normalized glycan value), $ρ$ parameter for strength of spatial dependency, $W$ the spatial weight matrix (=1 if neighbor, =0 else), $X$ additional covariates, $β$ parameters for strength of covariates, $ε$ error ($~N(0,\sigma^2I_n)$). $X$ includes the area per celltype in a pixel.
The parameters $\beta$ will then be used in the second stage of fitting.


```{r first_level_fit}
# level 1
column_names_fit1_template <- list(
  sample_name = "sample_id",
  celltypes = celltypes,
  value = "prop_maldi_area_filled",
  imsid = "ims_idx",
  coords = c("ims_x", "ims_y"),
  response = "mzval",
  covariate = NULL,
  sample_covariates = c("TMA_type", "Identifier", "sample_type","to_keep_reg")
)

fit1_common_args <- list(
  imcims_wide = data.table::copy(imcims_wide),
  n_workers = n_workers,
  column_names = column_names_fit1_template,
  method = "SAR",
  wmls_ls = wmls_ls,
  remove_na=TRUE,
  compress_fit  = TRUE,
  intercept = TRUE
)

fl <- create_formula("mz", column_names_fit1_template$celltypes, column_names_fit1_template$covariate, FALSE, intercept = fit1_common_args$intercept)
print("Formula:")
print(fl)

fit1ls <- lapply(mzcol_names, function(mzval) {
  cat(paste0("\n",mzval,"\n"))
  tmp_args <- fit1_common_args
  tmp_args$imcims_wide <- data.table::copy(imcims_wide)
  tmp_args$column_names$response <- mzval
  for (mztorm in mzcol_names[mzcol_names != mzval]){
    tmp_args$imcims_wide[,(mztorm) := NULL]
  }

  coef_mean <- mean(tmp_args$imcims_wide[[mzval]], na.rm = TRUE)
  coef_std <- sqrt(var(tmp_args$imcims_wide[[mzval]], na.rm=TRUE))
  tmp_args$imcims_wide[[mzval]] <- (tmp_args$imcims_wide[[mzval]]-coef_mean)/coef_std

  cat("\tfit: ")
  t1 <- Sys.time()
  out <- do.call(fit_first_layer, tmp_args)
  t2 <- Sys.time()
  out$coef_mean <- coef_mean
  out$coef_std <- coef_std
  cat(paste0(t2-t1, "\n"))
  tmpfitls <- list()
  tmpfitls[[mzval]][["fitls"]] <- out$fitls
  cat("\tpredict: ")
  t1 <- Sys.time()
  dfls <- get_predictions(tmpfitls, tmp_args$imcims_wide, wmls_ls, compress_fit = fit1_common_args$compress_fit)
  t2 <- Sys.time()
  cat(paste0(t2-t1, "\n"))
  dfdf <- data.table::as.data.table(do.call(rbind, dfls[[1]]))
  imcims_wide <- imcims_wide[dfdf, on = c("sample_id"="sample_id", "ims_idx"="ims_idx"), ] 
  out$fitls <- NULL
  out
})

names(fit1ls) <- mzcol_names
```



```{r save_data1}
tmpfit1ls <- fit1ls
tmpfit1ls$fitls <- NULL
saveRDS(tmpfit1ls, file.path(output_dir, "imc_to_ims_workflow_fit1ls_all_mz.rds"))
data.table::fwrite(imcims_wide, file.path(output_dir, "imc_to_ims_workflow_imcims_combined_full_wide.csv"))
```


# Session Info

```{r sessioninfo}
cat(paste0("Total Run time: ", purrr::reduce(all_times, `+`)))

print("Run times of chunks:")
print(all_times)

sessionInfo()
```
