---
title: "Glycans visualize associations"
author: "Reto Gerber"
date: "`r Sys.Date()`"
output: 
  html_document:
    self_contained: TRUE
    code_folding: "hide"
    toc: true
    toc_float: true
    toc_collapsed: true
toc_depth: 3
number_sections: true
theme: lumen
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 144, dev = "png")
all_times <- list() # store the time for each chunk
knitr::knit_hooks$set(time_it = local({
  now <- NULL
  function(before, options) {
    if (before) {
      now <<- Sys.time()
    } else {
      res <- difftime(Sys.time(), now)
      all_times[[options$label]] <<- round(lubridate::as.duration(res))
    }
  }
}))
knitr::opts_chunk$set(time_it = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
suppressPackageStartupMessages(suppressWarnings({
  library(ggplot2)
  library(ComplexHeatmap)
  library(SpatialExperiment)
}))
n_workers <- 10
RhpcBLASctl::blas_set_num_threads(n_workers)
data_dir_IMC <- "../../../../imc_workflow/results/spe/filt"
analysis_dir <- "."
output_dir <- "./output"
source(file.path(analysis_dir, "load_IMS.R"))
```

```{r}
colors_tma_type <- c("NASH_HCC_TMA" = "#BD9931FF", "cirrhosis_TMA" = "#EEE436FF")
colors_ims_pixelsize <- c(`10` = "#673821FF", `20` = "#BD9931FF", `30` = "#EEE436FF")
common_theme <- function(){
  theme_minimal() +
  theme(text=element_text(size=14))
}
```


# load data
```{r}
spe_compl <- readRDS(file.path(data_dir_IMC,"SPE_combined_03.rds"))
```
```{r}
fit2ls <- readRDS(file.path(output_dir, "imc_to_ims_workflow_fit2ls_all_mz_type.rds"))
```
```{r}
imcims_df_full <- data.table::fread(file.path(output_dir, "imc_to_ims_workflow_imcims_combined_full.csv"))
```
```{r}
mzvals <- stringr::str_split(names(fit2ls), "_", simplify = TRUE)[, 1]
regtype <- stringr::str_split(names(fit2ls), "_", simplify = TRUE)[, 2]

fit2ls <- fit2ls[regtype == "simple"]
mzvals <- stringr::str_split(names(fit2ls), "_", simplify = TRUE)[, 1]
names(fit2ls) <- mzvals

tmpls <- lapply(names(fit2ls), function(mz) {
  tmpdf <- fit2ls[[mz]]$fitdf
  tmpdf$mz <- mz
  tmpdf
  # dplyr::filter(tmpdf, effect == "fixed") |>
  #   dplyr::select(-effect, -group)
})
fitdf <- do.call(rbind, tmpls)
```

```{r}
celltype_proportions <- as.data.frame(colData(spe_compl)[,c("sample_id","celltype","project_name")]) |>
  dplyr::group_by(sample_id, celltype,project_name) |>
  dplyr::summarise(n = dplyr::n()) |>
  dplyr::group_by(sample_id) |>
  dplyr::mutate(p=n/sum(n)) 

celltype_proportions_filt <- celltype_proportions |>
  dplyr::left_join(unique(imcims_df_full[,c("to_keep_reg","sample_id")]), by = "sample_id") |>
  dplyr::filter(project_name %in% c("cirrhosis_TMA","NASH_HCC_TMA") & to_keep_reg) 

celltype_proportions_filt_mat <- tidyr::pivot_wider(celltype_proportions_filt, id_cols="sample_id",names_from="celltype", values_from = "p") |>
dplyr::ungroup() |>
dplyr::select(-sample_id) |>
as.matrix() 
```


```{r}
imcims_df_full <- imcims_df_full[imcims_df_full$to_keep_reg & imcims_df_full$in_IMC,]
is_mz_col <- stringr::str_detect(colnames(imcims_df_full), "[:digit:]{4}")
mzcol_names <- colnames(imcims_df_full)[is_mz_col]
mzcol_names <- mzcol_names[!mzcol_names %in% internal_standard_mz]
mzcol_names <- mzcol_names[mzcol_names %in% unique(fitdf$mz)]
imcims_df_full_px <- imcims_df_full |>
  dplyr::select(ims_idx, sample_id, dplyr::all_of(mzcol_names),region_type) |>
  dplyr::group_by(ims_idx, sample_id) |>
  unique()

imcims_prop_na <- imcims_df_full_px[,c("sample_id", mzcol_names)] |>
  dplyr::group_by(sample_id) |>
  dplyr::summarise(across(mzcol_names, ~sum(is.na(.x))/length(.x))) |>
  dplyr::select(-sample_id) |>
  as.matrix()

imcims_prop_na_region <- imcims_df_full_px[,c("sample_id", mzcol_names,"region_type")] |>
  dplyr::group_by(sample_id,region_type) |>
  dplyr::summarise(across(mzcol_names, ~sum(is.na(.x))/length(.x)), .groups = "drop") |>
  tidyr::complete(sample_id, region_type, fill = list(n = 0)) |>
  dplyr::select(-sample_id, -region_type) |>
  as.matrix()


imcims_intensity <- imcims_df_full_px[,c("sample_id", mzcol_names)] |>
  dplyr::group_by(sample_id) |>
  dplyr::summarise(across(mzcol_names, ~mean(na.omit(.x)))) |>
  dplyr::select(-sample_id) |>
  as.matrix()
```


# Results


The following table shows the results of the statistical testing. Column `reponse` is the celltype considered, `term` is either '(Intercept)' for average association, 'TMA_typeNASH_HCC_TMA' for condition specific association (i.e. Cirrhosis vs. NASH_HCC slides), 'sample_typeAdj' for difference in association between No Tumor (baseline) and Adjacent to Tumor samples, or 'sample_typeTumor' for differences in association between No Tumor (baseline) and Tumor samples, `mz` is the m/z value, `Estimate` is the strength of association (interpretation: if the IMS pixel is completely filled with this celltype, compared to absent, this is the expected change in glycan intensity), `FDR` is the p-value corrected for multiple testing.

```{r}
tmpdf <- fitdf
tmpdf$FDR <- signif(p.adjust(tmpdf$p.value, "fdr"), 2)
tmpdf$P.value <- signif(tmpdf$p.value, 2)
tmpdf$Std.error <- signif(tmpdf$std.error, 2)
tmpdf$Estimate <- signif(tmpdf$estimate, 2)
DT::datatable(tmpdf[, c("response", "term", "mz", "Estimate", "Std.error", "P.value", "FDR")],
  filter = "top",
  extensions = "Buttons",
  options = list(
    dom = "Blfrtip", pageLength = 30,
    buttons = c("copy", "csv", "excel", "pdf", "print")
  )
)
```

# Missingness

Proportion of missing IMS values per channel.

```{r}
imcims_df_full <- data.table::fread(file.path(output_dir, "imc_to_ims_workflow_imcims_combined_full.csv"))
imcims_df_full <- imcims_df_full[imcims_df_full$to_keep_reg,]
imcims_df_full$celltype[imcims_df_full$celltype==""] <- NA
is_mz_col <- stringr::str_detect(colnames(imcims_df_full), "[:digit:]{4}")
mzcol_names <- colnames(imcims_df_full)[is_mz_col]
mzcol_names <- mzcol_names[mzcol_names %in% unique(fitdf$mz)]
tdf <- is.na(imcims_df_full[,..mzcol_names])
pm <- colSums(tdf)/nrow(tdf)
round(pm*100,3)

tdf <- fitdf |>
  dplyr::mutate(FDR = p.adjust(p.value, "fdr")) |>
  dplyr::filter(term == "(Intercept)", response!="rho") |>
  dplyr::select(term, estimate, response, mz) |>
  tidyr::pivot_wider(names_from = "response", values_from = "estimate") |>
  dplyr::select(-term) |>
  tibble::column_to_rownames(var = "mz")

tdf <- cbind(data.frame(p_missing=pm),tdf)

celltypes <- unique(imcims_df_full$celltype)
celltypes <- celltypes[!is.na(celltypes)]
celltypes <- sort(celltypes)
```

## Missingness per celltype - estimates {.tabset}

Proportion of missing IMS values per channel vs the estimated association with the celltype.

```{r, results='asis'}
for(ct in celltypes){
cat(paste0("\n\n### ",ct,"\n\n"))
print(ggplot(tdf) +
  geom_point(aes(!!dplyr::sym(ct), p_missing), alpha = 0.75)) +
  labs(x = "Estimate", y = "Proportion missing")
}
```

## {-}

```{r}
tdf2 <- fitdf |>
  dplyr::mutate(logFDR = -log10(p.adjust(p.value, "fdr"))) |>
  dplyr::filter(term == "(Intercept)", response!="rho") |>
  dplyr::select(term, logFDR, response, mz) |>
  tidyr::pivot_wider(names_from = "response", values_from = "logFDR") |>
  dplyr::select(-term) |>
  tibble::column_to_rownames(var = "mz") 
tdf2 <- cbind(data.frame(p_missing=pm),tdf2)
```


## Missingness per celltype - -log10(FDR) {.tabset}

Proportion of missing IMS values per channel vs the log10 FDR corrected p-value for the association with the celltype.

```{r, results='asis'}
for(ct in celltypes){
cat(paste0("\n\n### ",ct,"\n\n"))
print(ggplot(tdf2) +
  geom_point(aes(!!dplyr::sym(ct), p_missing), alpha = 0.75)) +
  labs(x = "-log10(FDR)", y = "Proportion missing")
}
```

## Correlations between Missingness and Estimates/pvalues

Correlation of the proportion of missing IMS values per channel with the estimated association with the celltype and the log10 FDR corrected p-value for the association with the celltype.

```{r}
ec <- sapply(celltypes, function(ct) cor(tdf[[ct]], tdf$p_missing))
fc <- sapply(celltypes, function(ct) cor(tdf2[[ct]], tdf$p_missing))

cor_df <- data.frame(CellType = rep(celltypes, 2),
                     Estimate = c(ec, fc),
                     Metric = rep(c("Estimate", "-log10(FDR)"), each = length(celltypes)))
limit <- ceiling(max(abs(cor_df$Estimate))*10)/10
plt <- ggplot(cor_df, aes(x = Metric, y = CellType, fill = Estimate)) +
  geom_tile() +
  geom_text(aes(label = round(Estimate, 2))) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, limits=c(-limit, limit)) +
  labs(x = "", y = "", fill="Correlation") +
  theme_minimal()

plt
ggsave(file.path(data_dir,"paper","figures","Sfig_missingness_fitting.png"), plt,  width=5,height=6)
```


```{r}
tdf <- cbind(is.na(imcims_df_full[,..mzcol_names]),data.frame(sample_id = imcims_df_full$sample_id))
mismat <- dplyr::group_by(tdf, sample_id) |>
dplyr::summarise(dplyr::across(dplyr::all_of(mzcol_names), ~sum(.x)/dplyr::n())) |>
tibble::column_to_rownames(var = "sample_id") |>
as.matrix()

```

# Intercept {.tabset}

Estimated association of the average glycan intensity with the celltype. 'Estimate' is the strength of association (interpretation: if the IMS pixel is completely filled with this celltype, compared to absent/background, this is the expected change in glycan intensity), 'FDR' is the p-value corrected for multiple testing.


## Estimate

```{r, fig.width=8, fig.height=12}
mat <- fitdf |>
  dplyr::mutate(FDR = p.adjust(p.value, "fdr")) |>
  dplyr::filter(term == "(Intercept)", response!="rho") |>
  dplyr::select(term, estimate, response, mz) |>
  tidyr::pivot_wider(names_from = "response", values_from = "estimate") |>
  dplyr::select(-term) |>
  tibble::column_to_rownames(var = "mz") |>
  as.matrix()

c1 <- colorRampPalette(rev(RColorBrewer::brewer.pal(n = 9, name = "Blues")))(round(abs(min(na.omit(mat)))/diff(range(na.omit(mat)))*100))
c2 <- rev(colorRampPalette(rev(RColorBrewer::brewer.pal(n = 9, name = "Reds")))(round(abs(max(na.omit(mat)))/diff(range(na.omit(mat)))*100)))
co <- c(c1,c2)
tree_row <- pheatmap:::cluster_mat(mat, distance = "euclidean", method = "complete")
tree_col <- pheatmap:::cluster_mat(t(mat), distance = "euclidean", method = "complete")

hal = HeatmapAnnotation(
  `proportion\nmissing\nvalues` = anno_boxplot(t(imcims_prop_na), width = unit(0.75, "in"), outline=FALSE),
  `per sample\nmean\nintensity` = anno_boxplot(t(imcims_intensity), width = unit(0.75, "in"), outline=FALSE),
  which="row",
  gap = unit(0.1, "in")
  )
hat = HeatmapAnnotation(`celltype\nproportion` = anno_boxplot(celltype_proportions_filt_mat, height = unit(0.75, "in"), outline=FALSE), show_annotation_name = FALSE)
ht_opt$ROW_ANNO_PADDING = unit(0.1, "in")
phc1 <- ComplexHeatmap::Heatmap(mat, name="Estimate", col = co, cluster_rows = tree_row, cluster_columns = tree_col, column_names_rot = 90, column_title = "Estimate", top_annotation = hat, left_annotation = hal)
phc1
```

## -log10(FDR)

```{r, fig.width=8, fig.height=12}
mat2 <- fitdf |>
  dplyr::mutate(logFDR = -log10(p.adjust(p.value, "fdr"))) |>
  dplyr::filter(term == "(Intercept)", response!="rho") |>
  dplyr::select(term, logFDR, response, mz) |>
  tidyr::pivot_wider(names_from = "response", values_from = "logFDR") |>
  dplyr::select(-term) |>
  tibble::column_to_rownames(var = "mz") |>
  as.matrix()
c1 <- rep("#FFFFFF", round(100*((-log10(0.05))/max(na.omit(mat2)))))
c2 <- rev(colorRampPalette(rev(RColorBrewer::brewer.pal(n = 9, name = "Reds")))(round(100*(1-(-log10(0.05))/max(na.omit(mat2))))))
co2 <- c(c1,c2)
br <- seq(0,max(na.omit(mat2)),length.out=length(co)+1)

phc2 <- ComplexHeatmap::Heatmap(mat2, name="-log10(FDR)", col = co2, cluster_rows = tree_row, cluster_columns = tree_col, row_names_gp = gpar(fontsize = 8), column_names_rot = 90, column_title = "-log10(FDR)", top_annotation = hat)
phc2
```

## side by side

```{r, fig.width=14, fig.height=12}
plc <- phc1 + phc2
```

## Vulcano

```{r}
vulcano_plot <- function(df, filt_term, title){ 
df |>
dplyr::filter(term == filt_term) |>
dplyr::mutate(FDR = -log10(p.adjust(p.value, method = "fdr"))) |>
dplyr::mutate(is_sig = FDR > -log10(0.05)) |>
dplyr::mutate(name = paste0(mz, "\n", response)) |>
  ggplot() +
  geom_point(aes(estimate, FDR, color=response)) +
  geom_hline(yintercept = -log10(0.05), linetype = "dashed") +
  ggrepel::geom_label_repel(aes(estimate, FDR, label = name), size=2) +
  guides(colour = guide_legend(override.aes = list(size = 3))) +
  theme_minimal()
}
```

```{r, fig.width=10, fig.height=10}
fitdf |>
  dplyr::filter(term == "(Intercept)", response!="rho") |>
vulcano_plot("(Intercept)", "Association between celltypes and glycans")
```

## Missingness

```{r, fig.width=8, fig.height=12}
pheatmap::pheatmap(t(mismat),cluster_rows = tree_row)
```

# Session Info

```{r sessioninfo}
cat(paste0("Total Run time: ", purrr::reduce(all_times, `+`)))

print("Run times of chunks:")
print(all_times)

sessionInfo()
```
