---
title: "Visualize Filtering"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: FALSE 
    code_folding: "hide"
    toc: true
    toc_float: false 
    toc_collapsed: true
toc_depth: 3
number_sections: true
theme: lumen
editor_options:
  chunk_output_type: inline
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>


```{r}
basedir <- getwd()
# basedir <- "."
# tmp <- "results/{project_name}/data/registration_metric/report/{project_name}_registration_evaluation.html"
# basedir <- Reduce(file.path, rep("..",length(strsplit(dirname(snakemake@output[["html"]]),"/")[[1]])))

input_csv_files <- snakemake@input[["registration_metrics_combined"]]
project_name <- basename(dirname(dirname(dirname(input_csv_files))))
sample_names <- read.csv(input_csv_files[1])$sample

IMS_to_postIMS_svg <- sapply(snakemake@input[["IMS_to_postIMS_svg"]], function(s) file.path(basedir,s))

IMS_to_postIMS_png <- sapply(snakemake@input[["IMS_to_postIMS_png"]], function(s) file.path(basedir,s))

preIMSmask_to_postIMSmask_png <- sapply(snakemake@input[["preIMSmask_to_postIMSmask_png"]], function(s) file.path(basedir,s))

preIMCmask_to_preIMSmask_png <- sapply(snakemake@input[["preIMCmask_to_preIMSmask_png"]], function(s) file.path(basedir,s))

postIMCmask_to_preIMCmask_png <- sapply(snakemake@input[["postIMCmask_to_preIMCmask_png"]], function(s) file.path(basedir,s))

postIMCmask_to_postIMSmask_png <- sapply(snakemake@input[["postIMCmask_to_postIMSmask_png"]], function(s) file.path(basedir,s))

landmarks_postIMC_transformed_on_preIMC_png <- sapply(snakemake@input[["landmarks_postIMC_transformed_on_preIMC_png"]], function(s) file.path(basedir,s))
landmarks_preIMC_png <- sapply(snakemake@input[["landmarks_preIMC_png"]], function(s) file.path(basedir,s))

landmarks_preIMC_transformed_on_preIMS_png <- sapply(snakemake@input[["landmarks_preIMC_transformed_on_preIMS_png"]], function(s) file.path(basedir,s))
landmarks_preIMS_png <- sapply(snakemake@input[["landmarks_preIMS_png"]], function(s) file.path(basedir,s))

landmarks_preIMS_transformed_on_postIMS_png <- sapply(snakemake@input[["landmarks_preIMS_transformed_on_postIMS_png"]], function(s) file.path(basedir,s))
landmarks_postIMS_png <- sapply(snakemake@input[["landmarks_postIMS_png"]], function(s) file.path(basedir,s))

landmarks_postIMC_transformed_on_postIMS_png <- sapply(snakemake@input[["landmarks_postIMC_transformed_on_postIMS_png"]], function(s) file.path(basedir,s))
landmarks_postIMS_to_postIMC_png <- sapply(snakemake@input[["landmarks_postIMS_to_postIMC_png"]], function(s) file.path(basedir,s))

regions_postIMC_transformed_on_preIMC_png <- sapply(snakemake@input[["regions_postIMC_transformed_on_preIMC_png"]], function(s) file.path(basedir,s))
regions_preIMC_transformed_on_preIMS_png <- sapply(snakemake@input[["regions_preIMC_transformed_on_preIMS_png"]], function(s) file.path(basedir,s))
regions_preIMS_transformed_on_postIMS_png <- sapply(snakemake@input[["regions_preIMS_transformed_on_postIMS_png"]], function(s) file.path(basedir,s))
regions_postIMC_transformed_on_postIMS_png <- sapply(snakemake@input[["regions_postIMC_transformed_on_postIMS_png"]], function(s) file.path(basedir,s))

gif_postIMC_preIMC <- sapply(snakemake@input[["gif_postIMC_preIMC"]], function(s) file.path(basedir,s))
gif_postIMC_postIMS <- sapply(snakemake@input[["gif_postIMC_postIMS"]], function(s) file.path(basedir,s))
gif_preIMC_preIMS <- sapply(snakemake@input[["gif_preIMC_preIMS"]], function(s) file.path(basedir,s))
gif_preIMS_postIMS <- sapply(snakemake@input[["gif_preIMS_postIMS"]], function(s) file.path(basedir,s))
```


```{r, eval=FALSE}
basedir <- "/home/retger/Nextcloud/Projects/test_imc_to_ims_workflow/imc_to_ims_workflow"
# project_name <- "test_combined"
# sample_names <- c("Cirrhosis-TMA-5_New_Detector_001", "Cirrhosis-TMA-5_New_Detector_002")
input_csv_files <- "/home/retger/Downloads/cirrhosis_TMA_reg_metrics_combined.csv"
input_csv_files <- c("/home/retger/Nextcloud/Projects/test_imc_to_ims_workflow/imc_to_ims_workflow/results/test_combined/data/registration_metric/test_combined_reg_metrics_combined.csv")
input_csv_files <- "/home/retger/IMC/data/complete_analysis_imc_workflow/imc_to_ims_workflow/results/NASH_HCC_TMA/data/registration_metric/NASH_HCC_TMA_reg_metrics_combined.csv"
vis_type <- "IMS_to_postIMS"
```


```{r}
pairs_plot <- function(input_csv_files, vis_type, quantile_type="quantile50", return_missing=FALSE){
  stopifnot(quantile_type %in% c("mean","quantile05","quantile25","quantile50","quantile75","quantile95","min","max"))
  df <- read.csv(input_csv_files)
  colname_reg <- paste0(vis_type, "_")
  b1 <- stringr::str_detect(colnames(df), paste0("(^",vis_type,")|(_",vis_type,")"))
  t1 <- stringr::str_replace(vis_type,"_to_","_")
  b2 <- stringr::str_detect(colnames(df), paste0("(^",t1,")|(_",t1,")"))
  b3 <- colnames(df) %in% c("sample", "project")
  df <- df[, b1 | b2 | b3]
  colnames(df) <- stringr::str_replace(colnames(df), paste0(vis_type,"_"), "")
  colnames(df) <- stringr::str_replace(colnames(df), paste0("_",vis_type), "")
  colnames(df) <- stringr::str_replace(colnames(df), paste0("_",stringr::str_replace(vis_type,"_to_","_")), "")

  if(vis_type == "IMS_to_postIMS"){
    df$Completeness <- df$n_points/df$n_points_total
  }
  d <- plotly::highlight_key(df, ~sample)
  base <- plotly::plot_ly(
      d, 
      text = ~sample,
      # hoverinfo = "text",
      type = "scatter",
      mode = "markers",
      # color = 1,
      # colors = "Set1",
      marker = list(size = 10),
      showlegend = FALSE
  )
  pltls <- list()
  ismissing <- list(
    tissue_masks = rep(FALSE, nrow(df)),
    landmarks = rep(FALSE, nrow(df)),
    regions = rep(FALSE, nrow(df))
  )
  if("euclidean_distance_centroids" %in% colnames(df) & "dice_score" %in% colnames(df)){
  ismissing[["tissue_masks"]] <- is.na(df$euclidean_distance_centroids) | is.na(df$dice_score)
  masks_plt <- 
    plotly::add_markers(base, 
      x = ~euclidean_distance_centroids, 
      y = ~dice_score, 
      marker=list(color='rgb(0,0,0)'),
      hovertemplate = paste0('<b>%{text}</b><br>Error: %{x:.2f}<br>Dice: %{y:.2f}')) |>
      plotly::layout(
      xaxis = list(range=c(0,max(df$euclidean_distance_centroids)*1.1), title = "Distance between centroids"),
      yaxis = list(range=c(0,1.1),title = "Dice coefficient")
      ) |>
    plotly::add_annotations(
      text = "Tissue masks",
      x = 0.5,
      y = 1,
      yref = "paper",
      xref = "paper",
      xanchor = "middle",
      yanchor = "top",
      showarrow = FALSE,
      font = list(size = 15)
    )
  pltls <- c(pltls, list(masks_plt))
  }
  axis_type = paste0(quantile_type,"_error")
  if(axis_type %in% colnames(df) & "n_points_total" %in% colnames(df)){
  if(vis_type == "IMS_to_postIMS"){
    yaxis_type <- "Completeness"
    yaxis_title <- "Proportion of detected ablation marks"
    y_legend <- "Proportion"
  } else{
    yaxis_type <- "n_points_total"
    yaxis_title <- "Number of landmarks"
    y_legend <- "N landmarks"
  }
  ismissing[["landmarks"]] <- is.na(df[[axis_type]]) | is.na(df[[yaxis_type]])
  landmarks_plt <- 
    plotly::add_markers(base, 
      x = dplyr::quo(!!dplyr::sym(axis_type)), 
      y = dplyr::quo(!!dplyr::sym(yaxis_type)),
      marker=list(color='rgb(0,0,0)'),
      hovertemplate = sprintf('<b>%%{text}</b><br>Error: %%{x:.2f}<br>%s: %%{y:.2f}',y_legend)) |>
      plotly::layout(
      xaxis = list(range=c(0,max(df[[axis_type]])*1.1),title = "Distance between landmarks"),
      yaxis = list(range=c(0,max(df[[yaxis_type]])*1.1),title = yaxis_title)
    ) |>
    plotly::add_annotations(
      text = "Landmarks",
      x = 0.5,
      y = 1,
      yref = "paper",
      xref = "paper",
      xanchor = "middle",
      yanchor = "top",
      showarrow = FALSE,
      font = list(size = 15)
    )
  pltls <- c(pltls, list(landmarks_plt))
  }

  xaxis_type = paste0("regions_",quantile_type,"_error")
  yaxis_type = switch(quantile_type,
    "mean" = "regions_mean_dice",
    "quantile05" = "regions_quantile95_dice",
    "quantile25" = "regions_quantile75_dice",
    "quantile50" = "regions_quantile50_dice",
    "quantile75" = "regions_quantile25_dice",
    "quantile95" = "regions_quantile05_dice",
    "min" = "regions_max_dice",
    "max" = "regions_min_dice"
  )
  if(xaxis_type %in% colnames(df) & yaxis_type %in% colnames(df) & "regions_n_points_total" %in% colnames(df)){
  ismissing[["regions"]] <- is.na(df[[xaxis_type]]) | is.na(df[[yaxis_type]])
  regions_plt <- 
    plotly::add_markers(base, 
      x = dplyr::quo(!!dplyr::sym(xaxis_type)), 
      y = dplyr::quo(!!dplyr::sym(yaxis_type)), 
      color = ~regions_n_points_total,
      text = ~regions_n_points_total,
      hovertemplate = paste0('<b>%{text}</b><br>Error: %{x:.2f}<br>Dice: %{y:.2f}<br>N regions: %{text}')) |>
      plotly::layout(
      xaxis = list(range=c(0,max(df[[xaxis_type]])*1.1),title = "Distance between regions"),
      yaxis = list(range=c(0,1.1),title = "Dice coefficient")
    ) |>
    plotly::add_annotations(
      text = "Regions",
      x = 0.5,
      y = 1,
      yref = "paper",
      xref = "paper",
      xanchor = "middle",
      yanchor = "top",
      showarrow = FALSE,
      font = list(size = 15)
    )
  pltls <- c(pltls, list(regions_plt))
  }
  if(length(pltls)>0){
    fig <- plotly::subplot(
      pltls,
      titleX=TRUE,
      titleY=TRUE
      ) |>
      plotly::highlight(on = "plotly_hover", off = "plotly_doubleclick")
    if (return_missing) {
      missing_df <- data.frame(
        sample = df$sample,
        tissue_masks = ismissing[["tissue_masks"]],
        landmarks = ismissing[["landmarks"]],
        regions = ismissing[["regions"]]
      )
       return(list(fig, missing_df))
    } else{
    return(fig)
    }
  }else{
    return(NULL)
  }
}

```


```{r}
sitk_error_plot <- function(input_csv_files, vis_type="preIMS_to_postIMS"){
    colname_reg <- paste0(vis_type, "_")
    
    dfls <- lapply(input_csv_files, function(x) {
        df <- read.csv(x)
        df$project <- stringr::str_replace(basename(x),"_reg_metrics_combined.csv","")
        df <- df[,grepl(colname_reg, colnames(df)) | colnames(df) %in% c("sample", "project")]

        colnames(df) <- stringr::str_replace(colnames(df), colname_reg, "")
        colnames(df) <- stringr::str_replace(colnames(df),"quantile","Q" )
        df
    })
    df <- Reduce(rbind, dfls)

    # df$global_shift <- sqrt(colSums(rbind(df$global_x_shift**2, df$global_y_shift**2)))
    df$global_shift <- df$mean_error
    df$sitk_global_shift <- sqrt(colSums(rbind(df$sitk_global_x_shift**2, df$sitk_global_y_shift**2)))


    global_range <- range(unlist(lapply(colnames(df)[grepl("_shift",colnames(df))], function(x) df[[x]])))
    global_range[1] <- global_range[1]-1 
    global_range[2] <- global_range[2]+1

    d <- plotly::highlight_key(df, ~sample)
    base <- plotly::plot_ly(
        d, 
        text = ~sample,
        # hoverinfo = "text",
        type = "scatter",
        mode = "markers",
        color = ~project,
        colors = "Set1",
        marker = list(size = 10),
        showlegend = FALSE
    )
    fig <- plotly::subplot(
      plotly::add_markers(base, x = ~global_x_shift, y = ~sitk_global_x_shift,
        hovertemplate = paste0('<b>%{text}</b><br>X error Landmarks: %{y:.2f}<br>X error sitk: %{x:.2f}')) |>
        plotly::layout(
        xaxis = list(range=global_range, title = "X translation"),
        yaxis = list(range=global_range, title = "X translation sitk")
      ),
      plotly::add_markers(base, x = ~global_y_shift, y = ~sitk_global_y_shift,
        hovertemplate = paste0('<b>%{text}</b><br>Y error Landmarks: %{y:.2f}<br>Y error sitk: %{x:.2f}')) |>
        plotly::layout(
        xaxis = list(range=global_range, title = "Y translation"),
        yaxis = list(range=global_range, title = "Y translation sitk")
      ),
      plotly::add_markers(base, x = ~global_shift, y = ~sitk_global_shift,
        hovertemplate = paste0('<b>%{text}</b><br>Error Landmarks: %{y:.2f}<br>Error sitk: %{x:.2f}')) |>
        plotly::layout(
        xaxis = list(title = "translation"),
        yaxis = list(title = "translation sitk")
      )
    ) |> 
      plotly::add_annotations(
        text = "X translation",
        x = 0.15,
        y = 1,
        yref = "paper",
        xref = "paper",
        yanchor = "bottom",
        showarrow = FALSE,
        font = list(size = 15)
      ) |> 
      plotly::add_annotations(
        text = "Y translation",
        x = 0.5,
        y = 1,
        yref = "paper",
        xref = "paper",
        yanchor = "bottom",
        showarrow = FALSE,
        font = list(size = 15)
      ) |> 
      plotly::add_annotations(
        text = "Error",
        x = 0.85,
        y = 1,
        yref = "paper",
        xref = "paper",
        yanchor = "bottom",
        showarrow = FALSE,
        font = list(size = 15)
      ) |>
        plotly::layout(
        xaxis = list(title = "Landmarks"),
        yaxis = list(title = "sitk"),
        margin = list(t=50, b=150, l=50, r=50)
      ) |>
      plotly::highlight(on = "plotly_hover", off = "plotly_doubleclick")
    fig
}
```

```{r plot_images, results='asis', fig.width=8, fig.height=8, eval=FALSE, echo=FALSE}
cat("\n\n")
for (i in seq_along(filenames)) {
    filename <- filenames[i]
    if(file.exists(filename)){
        cat(sprintf("\n\n#### %s\n\n",sample_names[i]))
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" height=\"%s\"/>",filename,img_height))
    }
}
cat("\n\n")
```

```{r plot_2_images, results='asis', fig.width=8, fig.height=8, eval=FALSE, echo=FALSE}
cat("\n\n")
for (i in seq_along(filenames1)) {
    filename1 <- filenames1[i]
    filename2 <- filenames2[i]
    if(file.exists(filename1) & file.exists(filename2)){
        cat(sprintf("\n\n#### %s\n\n",sample_names[i]))
        cat("<p float=\"left\">")
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" width=\"50%%\"/>",filename1))
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" width=\"50%%\"/>",filename2))
        cat("</p>")
    }
}
cat("\n\n")
```


```{r pairs_plots, results='asis', fig.width=16, fig.height=8, echo=FALSE, eval=FALSE}
cat(sprintf("\n\n### %s\n\n","quantile50"))
tmp <- pairs_plot(input_csv_files, vis_type,"quantile50", return_missing=TRUE)
tmp[[1]]
is_missing <- tmp[[2]]$tissue_masks | tmp[[2]]$landmarks | tmp[[2]]$regions
if(sum(is_missing)>0){
    cat("\n\n")
    knitr::kable(tmp[[2]][is_missing,])
}
cat(sprintf("\n\n### %s\n\n","mean"))
tmp <- pairs_plot(input_csv_files, vis_type,"mean", return_missing=TRUE)
tmp[[1]]
is_missing <- tmp[[2]]$tissue_masks | tmp[[2]]$landmarks | tmp[[2]]$regions
if(sum(is_missing)>0){
    cat("\n\n")
    knitr::kable(tmp[[2]][is_missing,])
}
cat(sprintf("\n\n### %s\n\n","quantile05"))
tmp <- pairs_plot(input_csv_files, vis_type,"quantile05", return_missing=TRUE)
tmp[[1]]
is_missing <- tmp[[2]]$tissue_masks | tmp[[2]]$landmarks | tmp[[2]]$regions
if(sum(is_missing)>0){
    cat("\n\n")
    knitr::kable(tmp[[2]][is_missing,])
}
cat(sprintf("\n\n### %s\n\n","quantile95"))
tmp <- pairs_plot(input_csv_files, vis_type,"quantile95", return_missing=TRUE)
tmp[[1]]
is_missing <- tmp[[2]]$tissue_masks | tmp[[2]]$landmarks | tmp[[2]]$regions
if(sum(is_missing)>0){
    cat("\n\n")
    knitr::kable(tmp[[2]][is_missing,])
}
cat(sprintf("\n\n### %s\n\n","min"))
tmp <- pairs_plot(input_csv_files, vis_type,"min", return_missing=TRUE)
tmp[[1]]
is_missing <- tmp[[2]]$tissue_masks | tmp[[2]]$landmarks | tmp[[2]]$regions
if(sum(is_missing)>0){
    cat("\n\n")
    knitr::kable(tmp[[2]][is_missing,])
}
cat(sprintf("\n\n### %s\n\n","max"))
tmp <- pairs_plot(input_csv_files, vis_type,"max", return_missing=TRUE)
tmp[[1]]
is_missing <- tmp[[2]]$tissue_masks | tmp[[2]]$landmarks | tmp[[2]]$regions
if(sum(is_missing)>0){
    cat("\n\n")
    knitr::kable(tmp[[2]][is_missing,])
}
cat("\n\n")
```

# Overview
```{r}
min_completenes <- 0.1
min_landmarks <- 50
min_regions <- 2
min_q50_error <- 5
min_q50_dice <- 0.7
```
```{r}
df <- read.csv(input_csv_files)

df$IMS_Completeness <- df$IMS_to_postIMS_n_points/df$IMS_to_postIMS_n_points_total

IMS_error_thr <- median(df$IMS_to_postIMS_quantile50_error)+3*mad(df$IMS_to_postIMS_quantile50_error)
keep_IMS_to_postIMS <- df$IMS_Completeness > min_completenes & df$IMS_to_postIMS_quantile50_error < IMS_error_thr

## postIMC to postIMS
### landmarks
postIMCpostIMS_lm <- rep(NA, length(df$sample))
postIMCpostIMS_lm[df$postIMC_to_postIMS_n_points_total > min_landmarks] <- df$postIMC_to_postIMS_quantile50_error[df$postIMC_to_postIMS_n_points_total > min_landmarks] < min_q50_error

### regions
postIMCpostIMS_reg <- rep(NA, length(df$sample))
postIMCpostIMS_reg[df$postIMC_to_postIMS_regions_n_points_total > min_regions] <- 
df$postIMC_to_postIMS_regions_quantile50_error[df$postIMC_to_postIMS_regions_n_points_total > min_regions] < min_q50_error &
df$postIMC_to_postIMS_regions_quantile50_dice[df$postIMC_to_postIMS_regions_n_points_total > min_regions] > min_q50_dice

## preIMS to postIMS
### landmarks
preIMSpostIMS_lm <- rep(NA, length(df$sample))
preIMSpostIMS_lm[df$preIMS_to_postIMS_n_points_total > min_landmarks] <- df$preIMS_to_postIMS_quantile50_error[df$preIMS_to_postIMS_n_points_total > min_landmarks] < min_q50_error

### regions
preIMSpostIMS_reg <- rep(NA, length(df$sample))
preIMSpostIMS_reg[df$preIMS_to_postIMS_regions_n_points_total > min_regions] <- 
df$preIMS_to_postIMS_regions_quantile50_error[df$preIMS_to_postIMS_regions_n_points_total > min_regions] < min_q50_error |
df$preIMS_to_postIMS_regions_quantile50_dice[df$preIMS_to_postIMS_regions_n_points_total > min_regions] > min_q50_dice

### sitk
preIMSpostIMS_sitk <- sqrt(df$preIMS_to_postIMS_sitk_global_x_shift**2 + df$preIMS_to_postIMS_sitk_global_y_shift**2) < min_q50_error

## preIMC to preIMS
### landmarks
preIMCpreIMS_lm <- rep(NA, length(df$sample))
preIMCpreIMS_lm[df$preIMC_to_preIMS_n_points_total > min_landmarks] <- df$preIMC_to_preIMS_quantile50_error[df$preIMC_to_preIMS_n_points_total > min_landmarks] < min_q50_error

### regions
preIMCpreIMS_reg <- rep(NA, length(df$sample))
preIMCpreIMS_reg[df$preIMC_to_preIMS_regions_n_points_total > min_regions] <- 
df$preIMC_to_preIMS_regions_quantile50_error[df$preIMC_to_preIMS_regions_n_points_total > min_regions] < min_q50_error |
df$preIMC_to_preIMS_regions_quantile50_dice[df$preIMC_to_preIMS_regions_n_points_total > min_regions] > min_q50_dice

## postIMC to preIMC
### landmarks
postIMCpreIMC_lm <- rep(NA, length(df$sample))
postIMCpreIMC_lm[df$postIMC_to_preIMC_n_points_total > min_landmarks] <- df$postIMC_to_preIMC_quantile50_error[df$postIMC_to_preIMC_n_points_total > min_landmarks] < min_q50_error

### regions
postIMCpreIMC_reg <- rep(NA, length(df$sample))
postIMCpreIMC_reg[df$postIMC_to_preIMC_regions_n_points_total > min_regions] <- 
df$postIMC_to_preIMC_regions_quantile50_error[df$postIMC_to_preIMC_regions_n_points_total > min_regions] < min_q50_error |
df$postIMC_to_preIMC_regions_quantile50_dice[df$postIMC_to_preIMC_regions_n_points_total > min_regions] > min_q50_dice

```
```{r}
to_keep_df <- data.frame(
    sample = df$sample,
    IMS_to_postIMS = keep_IMS_to_postIMS,
    postIMCpostIMS_lm = postIMCpostIMS_lm,
    postIMCpostIMS_reg = postIMCpostIMS_reg,
    preIMSpostIMS_lm = preIMSpostIMS_lm,
    preIMSpostIMS_reg = preIMSpostIMS_reg,
    preIMSpostIMS_sitk = preIMSpostIMS_sitk,
    preIMCpreIMS_lm = preIMCpreIMS_lm,
    preIMCpreIMS_reg = preIMCpreIMS_reg,
    postIMCpreIMC_lm = postIMCpreIMC_lm,
    postIMCpreIMC_reg = postIMCpreIMC_reg
)
```

```{r}
postIMC_to_postIMS = ifelse(is.na(postIMCpostIMS_lm),FALSE,postIMCpostIMS_lm) | ifelse(is.na(postIMCpostIMS_reg),FALSE,postIMCpostIMS_reg)
postIMC_to_postIMS[!postIMC_to_postIMS][is.na(postIMCpostIMS_lm[!postIMC_to_postIMS]) & is.na(postIMCpostIMS_reg[!postIMC_to_postIMS])] <- NA

preIMS_to_postIMS = ifelse(is.na(preIMSpostIMS_lm),FALSE,preIMSpostIMS_lm) | ifelse(is.na(preIMSpostIMS_reg),FALSE,preIMSpostIMS_reg) | ifelse(is.na(preIMSpostIMS_sitk),FALSE,preIMSpostIMS_sitk)
preIMS_to_postIMS[!preIMS_to_postIMS][is.na(preIMSpostIMS_lm[!preIMS_to_postIMS]) & is.na(preIMSpostIMS_reg[!preIMS_to_postIMS])] <- NA

preIMC_to_preIMS = ifelse(is.na(preIMCpreIMS_lm),FALSE,preIMCpreIMS_lm) | ifelse(is.na(preIMCpreIMS_reg),FALSE,preIMCpreIMS_reg)
preIMC_to_preIMS[!preIMC_to_preIMS][is.na(preIMCpreIMS_lm[!preIMC_to_preIMS]) & is.na(preIMCpreIMS_reg[!preIMC_to_preIMS])] <- NA

postIMC_to_preIMC = ifelse(is.na(postIMCpreIMC_lm),FALSE,postIMCpreIMC_lm) | ifelse(is.na(postIMCpreIMC_reg),FALSE,postIMCpreIMC_reg)
postIMC_to_preIMC[!postIMC_to_preIMC][is.na(postIMCpreIMC_lm[!postIMC_to_preIMC]) & is.na(postIMCpreIMC_reg[!postIMC_to_preIMC])] <- NA

t1 <- (keep_IMS_to_postIMS & preIMS_to_postIMS & preIMC_to_preIMS & postIMC_to_preIMC)
to_keep_overall <- ifelse(is.na(t1),FALSE,t1) | ifelse(is.na(postIMC_to_postIMS),FALSE,postIMC_to_postIMS)
to_keep_overall[!to_keep_overall][is.na(t1[!to_keep_overall]) | is.na(postIMC_to_postIMS[!to_keep_overall])] <- NA

to_keep_df_aggr <- data.frame(
  sample = df$sample,
  IMS_to_postIMS = keep_IMS_to_postIMS,
  postIMC_to_postIMS = postIMC_to_postIMS,
  preIMS_to_postIMS = preIMS_to_postIMS,
  preIMC_to_preIMS = preIMC_to_preIMS,
  postIMC_to_preIMC = postIMC_to_preIMC,
  overall = to_keep_overall
)
```

## Summarized results

The following heatmap is a summary of the results. The columns are the different registration steps and the rows are the samples. The color of the cells indicate whether the registration step was successful or not. The used thresholds are: 

| Threshold                                  | Value         |
|:-------------------------------------------|:--------------|
| Minimum completeness IMS ablation marks    | `r min_completenes` |
| Minimum number of landmarks                | `r min_landmarks`    |
| Minimum number of regions                  | `r min_regions`      |
| Maximum error (quantile 50)                | `r min_q50_error`    |
| Minimum Dice coefficient (quantile 50)     | `r min_q50_dice`     |

This evaluation is rather strict meaning that if the 'overall' column is TRUE, the sample is likely to be registered well. However, if the 'overall' column is FALSE or NA, it does not necessarily mean that the sample is not registered well. Therefore it is adviced to check the FALSE and NA entries in the additional plots and images below. 

```{r, fig.width=12, fig.height=8}
data_long <- tidyr::pivot_longer(to_keep_df_aggr, c("IMS_to_postIMS","postIMC_to_postIMS","preIMS_to_postIMS","preIMC_to_preIMS","postIMC_to_preIMC","overall"))
data_long$name <- factor(data_long$name,c("IMS_to_postIMS","preIMS_to_postIMS","preIMC_to_preIMS","postIMC_to_preIMC","postIMC_to_postIMS","overall"))

ggplot2::ggplot(data_long,ggplot2::aes(name, sample, fill = value)) +
  ggplot2::geom_tile() +
  ggplot2::labs(x = NULL, y = NULL, fill="keep") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) 
```

# IMS to postIMS

## Images

### Ablation marks & registered IMS pixels {.tabset}

The images shown below are the ablation marks (from the postIMS microscopy image) and the IMS pixels (from the IMS image) after registration. 
Color legend for the below images:

| Color | Description  |
|-------|--------------|
| Blue  | Ablation marks |
| Green | IMS pixel    |

```{r}
tthr <- median(df$IMS_to_postIMS_quantile50_error)+mad(df$IMS_to_postIMS_quantile50_error)
df$IMS_to_postIMS_show_image <- df$IMS_to_postIMS_quantile50_error > tthr

bn <- basename(IMS_to_postIMS_svg)
bn <- stringr::str_replace(bn,"_IMS_to_postIMS_combined_registration_all.svg","")
project_name <- basename(dirname(dirname(dirname(dirname(IMS_to_postIMS_svg[1])))))
bn <- stringr::str_replace(bn,paste0(project_name,"_"),"")
tdf <- dplyr::right_join(df, data.frame(sample=bn, filename=IMS_to_postIMS_svg), by="sample")

filenames <- dplyr::filter(tdf, IMS_to_postIMS_show_image)$filename
sample_names_cp <- sample_names
sample_names <- dplyr::filter(tdf, IMS_to_postIMS_show_image)$sample
img_height=1000
```
```{r plot_images_IMS_to_postIMS, ref.label='plot_images', results='asis'}
```
```{r}
sample_names <- sample_names_cp
```
## Distances ablation marks to IMS pixels {.tabset}

The plot below shows the distances (mean, median, etc.) on the x-axis versus the completeness (number of detected ablation marks divided by the total number of IMS pixels) on the y-axis.

```{r}
vis_type <- "IMS_to_postIMS"
```
```{r pairs_plots_IMS_to_postIMS, ref.label='pairs_plots', results='asis', fig.width=7, fig.height=7}
```


# postIMC to postIMS

## Summary plots of the registration metrics {.tabset}

| Position | Measure | x-axis | y-axis | color  | 
|:---------|:--------|:-------|:-------|:-------|
| Left     | Tissue masks | Distance between centroids | Dice coefficient | |
| Middle   | Landmarks | Summarized distance between landmarks | Number of landmarks | |
| Right    | Regions | Summarized distance between regions | Dice coefficients | Number of regions |


```{r}
vis_type <- "postIMC_to_postIMS"
imgtype1 <- stringr::str_split(vis_type,"_to_")[[1]][1]
imgtype2 <- stringr::str_split(vis_type,"_to_")[[1]][2]
```
```{r pairs_plots_postIMC_to_postIMS, ref.label='pairs_plots', results='asis', fig.width=12, fig.height=7}
```


## Images {.tabset}

### Tissue masks {.tabset}

Shown below are the masks of the tissue masks, overlayed on top of each other. Extraction of the tissue masks is not always exact (especially for the postIMS images), so the results might be unreliable.
Color legend for the below images:

| Color | Description |
|-------|-------------|
| Black | Neither     |
| Dark gray  | `r imgtype1` only |
| Light gray  | `r imgtype2` only |
| White | Both        |

```{r}
filenames <- postIMCmask_to_postIMSmask_png
img_height=700
```
```{r plot_images_postIMC_to_postIMS_mask, ref.label='plot_images', results='asis'}
```

### Images of Landmarks {.tabset}

Below are shown the landmarks from the `r imgtype1` image (left) and the `r imgtype2` image (right) after registration. The landmarks are shown as errors where the start of the arrow is on the respective image and the end is the corresponding landmark in the other image. The length of the arrows are therefore the distance between individual landmarks. 

|left | right|
|:----|:-----|
|`r imgtype1` | `r imgtype2` |


```{r}
filenames1 <- landmarks_postIMC_transformed_on_postIMS_png
filenames2 <- landmarks_postIMS_to_postIMC_png
```
```{r plot_2_images_preIMS_to_postIMS_landmarks, ref.label='plot_2_images', results='asis', fig.width=8, fig.height=8}
```



### Images of Regions {.tabset}

Below are shown the regions from the `r imgtype1` image (left) and the `r imgtype2` image (right) after registration. 

| Color | Description |
|-------|-------------|
| Black | Neither     |
| Dark gray  | `r imgtype1` only |
| Light gray  | `r imgtype2` only |
| White | Both        |


```{r}
filenames <- regions_postIMC_transformed_on_postIMS_png
img_height=700
```
```{r plot_images_postIMC_to_postIMS_regions, ref.label='plot_images', results='asis'}
```

### Overlayed {.tabset}

```{r}
filenames <- gif_postIMC_postIMS
img_height=100
```
```{r plot_images_postIMC_to_postIMS_gif, ref.label='plot_images', results='asis'}
```



# preIMS to postIMS

## Summary plots of the registration metrics {.tabset}

| Position | Measure | x-axis | y-axis | color  | 
|:---------|:--------|:-------|:-------|:-------|
| Left     | Tissue masks | Distance between centroids | Dice coefficient | |
| Middle   | Landmarks | Summarized distance between landmarks | Number of landmarks | |
| Right    | Regions | Summarized distance between regions | Dice coefficients | Number of regions |


```{r}
vis_type <- "preIMS_to_postIMS"
imgtype1 <- stringr::str_split(vis_type,"_to_")[[1]][1]
imgtype2 <- stringr::str_split(vis_type,"_to_")[[1]][2]
```
```{r pairs_plots_preIMS_to_postIMS, ref.label='pairs_plots', results='asis', fig.width=15, fig.height=7}
```

## Images {.tabset}

### Tissue masks {.tabset}

Shown below are the masks of the tissue masks, overlayed on top of each other. Extraction of the tissue masks is not always exact (especially for the postIMS images), so the results might be unreliable.
Color legend for the below images:

| Color | Description |
|-------|-------------|
| Black | Neither     |
| Dark gray  | `r imgtype1` only |
| Light gray  | `r imgtype2` only |
| White | Both        |

```{r}
filenames <- preIMSmask_to_postIMSmask_png
img_height=700
```
```{r plot_images_preIMS_to_postIMS_mask, ref.label='plot_images', results='asis'}
```

### Images of Landmarks {.tabset}

Below are shown the landmarks from the `r imgtype1` image (left) and the `r imgtype2` image (right) after registration. The landmarks are shown as errors where the start of the arrow is on the respective image and the end is the corresponding landmark in the other image. The length of the arrows are therefore the distance between individual landmarks. 

|left | right|
|:----|:-----|
|`r imgtype1` | `r imgtype2` |


```{r}
filenames1 <- landmarks_preIMS_transformed_on_postIMS_png
filenames2 <- landmarks_postIMS_png
```
```{r plot_2_images_preIMS_to_postIMS_landmarks, ref.label='plot_2_images', results='asis', fig.width=8, fig.height=8}
```

### Images of Regions {.tabset}

Below are shown the regions from the `r imgtype1` image (left) and the `r imgtype2` image (right) after registration. 

| Color | Description |
|-------|-------------|
| Black | Neither     |
| Dark gray  | `r imgtype1` only |
| Light gray  | `r imgtype2` only |
| White | Both        |


```{r}
filenames <- regions_preIMS_transformed_on_postIMS_png
img_height=700
```
```{r plot_images_preIMS_to_postIMS_regions, ref.label='plot_images', results='asis'}
```

### Overlayed {.tabset}

```{r}
filenames <- gif_preIMS_postIMS
img_height=100
```
```{r plot_images_preIMS_to_postIMS_gif, ref.label='plot_images', results='asis'}
```


## Translations based on grid subtracted postIMS to preIMS registration

The plot below shows the translations (x and y) based on the grid subtracted postIMS to preIMS registration (using image intensities). The leftmost plot shows the translation in the X direction with the x-axis representing the infered translation from the landmarks and the y-axis the infered translation from the grid subtracted registration. The middle plot shows the same but in the Y direction. The rightmost plot shows the global translation (sqrt(x^2+y^2)) with the x-axis representing the infered translation from the landmarks and the y-axis the infered translation from the grid subtracted registration.


```{r, fig.width=10, fig.height=5}
fig <- sitk_error_plot(input_csv_files, "preIMS_to_postIMS")
fig
```


# preIMC to preIMS

## Summary plots of the registration metrics {.tabset}

| Position | Measure | x-axis | y-axis | color  | 
|:---------|:--------|:-------|:-------|:-------|
| Left     | Tissue masks | Distance between centroids | Dice coefficient | |
| Middle   | Landmarks | Summarized distance between landmarks | Number of landmarks | |
| Right    | Regions | Summarized distance between regions | Dice coefficients | Number of regions |


```{r}
vis_type <- "preIMC_to_preIMS"
imgtype1 <- stringr::str_split(vis_type,"_to_")[[1]][1]
imgtype2 <- stringr::str_split(vis_type,"_to_")[[1]][2]
```
```{r pairs_plots_preIMC_to_preIMS, ref.label='pairs_plots', results='asis', fig.width=15, fig.height=7}
```


## Images {.tabset}

### Tissue masks {.tabset}

Shown below are the masks of the tissue masks, overlayed on top of each other. Extraction of the tissue masks is not always exact (especially for the postIMS images), so the results might be unreliable.
Color legend for the below images:

| Color | Description |
|-------|-------------|
| Black | Neither     |
| Dark gray  | `r imgtype1` only |
| Light gray  | `r imgtype2` only |
| White | Both        |

```{r}
filenames <- preIMCmask_to_preIMSmask_png
img_height=700
```
```{r plot_images_preIMC_to_preIMS_mask, ref.label='plot_images', results='asis'}
```

### Images of Landmarks {.tabset}

Below are shown the landmarks from the `r imgtype1` image (left) and the `r imgtype2` image (right) after registration. The landmarks are shown as errors where the start of the arrow is on the respective image and the end is the corresponding landmark in the other image. The length of the arrows are therefore the distance between individual landmarks. 

|left | right|
|:----|:-----|
|`r imgtype1` | `r imgtype2` |


```{r}
filenames1 <- landmarks_preIMC_transformed_on_preIMS_png
filenames2 <- landmarks_preIMS_png
```
```{r plot_2_images_preIMC_to_preIMS_landmarks, ref.label='plot_2_images', results='asis', fig.width=8, fig.height=8}
```

### Images of Regions {.tabset}

Below are shown the regions from the `r imgtype1` image (left) and the `r imgtype2` image (right) after registration. 

| Color | Description |
|-------|-------------|
| Black | Neither     |
| Dark gray  | `r imgtype1` only |
| Light gray  | `r imgtype2` only |
| White | Both        |


```{r}
filenames <- regions_preIMC_transformed_on_preIMS_png
img_height=700
```
```{r plot_images_preIMC_to_preIMS_regions, ref.label='plot_images', results='asis'}
```

### Overlayed {.tabset}

```{r}
filenames <- gif_preIMC_preIMS
img_height=100
```
```{r plot_images_preIMC_to_preIMS_gif, ref.label='plot_images', results='asis'}
```



# postIMC to preIMC

## Summary plots of the registration metrics {.tabset}

| Position | Measure | x-axis | y-axis | color  | 
|:---------|:--------|:-------|:-------|:-------|
| Left     | Tissue masks | Distance between centroids | Dice coefficient | |
| Middle   | Landmarks | Summarized distance between landmarks | Number of landmarks | |
| Right    | Regions | Summarized distance between regions | Dice coefficients | Number of regions |


```{r}
vis_type <- "postIMC_to_preIMC"
imgtype1 <- stringr::str_split(vis_type,"_to_")[[1]][1]
imgtype2 <- stringr::str_split(vis_type,"_to_")[[1]][2]
```
```{r pairs_plots_postIMC_to_preIMC, ref.label='pairs_plots', results='asis', fig.width=15, fig.height=7}
```


## Images {.tabset}

### Tissue masks {.tabset}

Shown below are the masks of the tissue masks, overlayed on top of each other. Extraction of the tissue masks is not always exact (especially for the postIMS images), so the results might be unreliable.
Color legend for the below images:

| Color | Description |
|-------|-------------|
| Black | Neither     |
| Dark gray  | `r imgtype1` only |
| Light gray  | `r imgtype2` only |
| White | Both        |

```{r}
filenames <- postIMCmask_to_preIMCmask_png
img_height=700
```
```{r plot_images_postIMC_to_preIMC_mask, ref.label='plot_images', results='asis'}
```

### Images of Landmarks {.tabset}

Below are shown the landmarks from the `r imgtype1` image (left) and the `r imgtype2` image (right) after registration. The landmarks are shown as errors where the start of the arrow is on the respective image and the end is the corresponding landmark in the other image. The length of the arrows are therefore the distance between individual landmarks. 

|left | right|
|:----|:-----|
|`r imgtype1` | `r imgtype2` |


```{r}
filenames1 <- landmarks_postIMC_transformed_on_preIMC_png
filenames2 <- landmarks_preIMC_png
```
```{r plot_2_images_postIMC_to_preIMC_landmarks, ref.label='plot_2_images', results='asis', fig.width=8, fig.height=8}
```

### Images of Regions {.tabset}

Below are shown the regions from the `r imgtype1` image (left) and the `r imgtype2` image (right) after registration. 

| Color | Description |
|-------|-------------|
| Black | Neither     |
| Dark gray  | `r imgtype1` only |
| Light gray  | `r imgtype2` only |
| White | Both        |


```{r}
filenames <- regions_postIMC_transformed_on_preIMC_png
img_height=700
```
```{r plot_images_postIMC_to_preIMC_regions, ref.label='plot_images', results='asis'}
```


### Overlayed {.tabset}

```{r}
filenames <- gif_postIMC_preIMC
img_height=100
```
```{r plot_images_postIMC_to_preIMC_gif, ref.label='plot_images', results='asis'}
```

