---
title: "Visualize Filtering"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: FALSE 
    code_folding: "hide"
    toc: true
    toc_float: false 
    toc_collapsed: true
toc_depth: 3
number_sections: true
theme: lumen
editor_options:
  chunk_output_type: inline
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>


```{r}
basedir <- getwd()
# basedir <- "."
# tmp <- "results/{project_name}/data/registration_metric/report/{project_name}_registration_evaluation.html"
# basedir <- Reduce(file.path, rep("..",length(strsplit(dirname(snakemake@output[["html"]]),"/")[[1]])))

input_csv_files <- snakemake@input[["registration_metrics_combined"]]
project_name <- basename(dirname(dirname(dirname(input_csv_files))))
sample_names <- read.csv(input_csv_files[1])$sample

IMS_to_postIMS_svg <- sapply(snakemake@input[["IMS_to_postIMS_svg"]], function(s) file.path(basedir,s))

IMS_to_postIMS_png <- sapply(snakemake@input[["IMS_to_postIMS_png"]], function(s) file.path(basedir,s))

preIMSmask_to_postIMSmask_png <- sapply(snakemake@input[["preIMSmask_to_postIMSmask_png"]], function(s) file.path(basedir,s))

preIMCmask_to_preIMSmask_png <- sapply(snakemake@input[["preIMCmask_to_preIMSmask_png"]], function(s) file.path(basedir,s))

postIMCmask_to_preIMCmask_png <- sapply(snakemake@input[["postIMCmask_to_preIMCmask_png"]], function(s) file.path(basedir,s))

landmarks_postIMC_transformed_on_preIMC_png <- sapply(snakemake@input[["landmarks_postIMC_transformed_on_preIMC_png"]], function(s) file.path(basedir,s))
landmarks_preIMC_png <- sapply(snakemake@input[["landmarks_preIMC_png"]], function(s) file.path(basedir,s))

landmarks_preIMC_transformed_on_preIMS_png <- sapply(snakemake@input[["landmarks_preIMC_transformed_on_preIMS_png"]], function(s) file.path(basedir,s))
landmarks_preIMS_png <- sapply(snakemake@input[["landmarks_preIMS_png"]], function(s) file.path(basedir,s))

landmarks_preIMS_transformed_on_postIMS_png <- sapply(snakemake@input[["landmarks_preIMS_transformed_on_postIMS_png"]], function(s) file.path(basedir,s))
landmarks_postIMS_png <- sapply(snakemake@input[["landmarks_postIMS_png"]], function(s) file.path(basedir,s))
```


```{r}
# basedir <- "/home/retger/Nextcloud/Projects/test_imc_to_ims_workflow/imc_to_ims_workflow"
# project_name <- "test_combined"
# sample_names <- c("Cirrhosis-TMA-5_New_Detector_001", "Cirrhosis-TMA-5_New_Detector_002")
# input_csv_files <- c("/home/retger/Nextcloud/Projects/test_imc_to_ims_workflow/imc_to_ims_workflow/results/test_combined/data/registration_metric/test_combined_reg_metrics_combined.csv")
```

```{r}
create_error_plot <- function(input_csv_files, vis_type){
    colname_reg <- paste0(vis_type, "_")
    
    dfls <- lapply(input_csv_files, function(x) {
        df <- read.csv(x)
        df$project <- stringr::str_replace(basename(x),"_reg_metrics_combined.csv","")
        df <- df[,grepl(colname_reg, colnames(df)) | colnames(df) %in% c("sample", "project")]
    
        colnames(df) <- stringr::str_replace(colnames(df), colname_reg, "")
        colnames(df) <- stringr::str_replace(colnames(df),"quantile","Q" )
        df
    })
    df <- Reduce(rbind, dfls)
    
    x_axis_var_names <- colnames(df)[grepl("error", colnames(df))]
    create_buttons <- function(df, x_axis_var_names) {
      lapply(
        x_axis_var_names,
        FUN = function(var_name, df) {
          button <- list(
            method = 'restyle',
            args = list('x', list(df[, var_name])),
            label = stringr::str_to_title(stringr::str_replace(var_name,"_"," "))
          )
        },
        df
      )
    }
    
    global_x_range <- range(unlist(lapply(x_axis_var_names, function(x) df[[x]])))
    global_x_range[1] <- 0 
    global_x_range[2] <- global_x_range[2]+2
    
    if (vis_type == "IMS_to_postIMS") {
      df$completeness <- df$n_points/df$n_points_total
      y_axis_colname <- "completeness"
      y_axis_name <- "Completeness"
    } else {
      y_axis_colname <- "n_points_total"
      y_axis_name <- "Number of Landmarks"
    }
    
    dfls <- split(df, df$project)
    figls <- lapply(dfls, function(df){
        plotly::plot_ly(
            data = df,
            x = ~mean_error,
            y = dplyr::quo(!!dplyr::sym(y_axis_colname)),
            text = ~sample,
            # hoverinfo = "text",
            hovertemplate = paste0('<b>%{text}</b><br>',y_axis_name,': %{y:.2f}<br>Error: %{x:.2f}'),
            type = "scatter",
            mode = "markers",
            color = ~project,
            colors = "Set1",
            marker = list(size = 10)
        ) |>
             plotly::layout(
                 title = paste0(stringr::str_replace_all(vis_type,"_"," "),":   Error vs ",y_axis_name),
                 xaxis = list(domain = c(0.1, 1), range=global_x_range, title = ""),
                 yaxis = list(title = y_axis_name),
                 updatemenus = list(
                     list(
                         y = -0.05,
                         x = 0.5,
                         buttons = create_buttons(df, x_axis_var_names)
                     )
                 )
                 )
    })
    fig <- plotly::subplot(figls, nrows = 1, shareX = TRUE, shareY = TRUE) |>
        plotly::layout(margin = list(t=50, b=150, l=50, r=50))
    fig
}


sitk_error_plot <- function(input_csv_files, vis_type="preIMS_to_postIMS"){
    colname_reg <- paste0(vis_type, "_")
    
    dfls <- lapply(input_csv_files, function(x) {
        df <- read.csv(x)
        df$project <- stringr::str_replace(basename(x),"_reg_metrics_combined.csv","")
        df <- df[,grepl(colname_reg, colnames(df)) | colnames(df) %in% c("sample", "project")]

        colnames(df) <- stringr::str_replace(colnames(df), colname_reg, "")
        colnames(df) <- stringr::str_replace(colnames(df),"quantile","Q" )
        df
    })
    df <- Reduce(rbind, dfls)

    # df$global_shift <- sqrt(colSums(rbind(df$global_x_shift**2, df$global_y_shift**2)))
    df$global_shift <- df$mean_error
    df$sitk_global_shift <- sqrt(colSums(rbind(df$sitk_global_x_shift**2, df$sitk_global_y_shift**2)))


    global_range <- range(unlist(lapply(colnames(df)[grepl("_shift",colnames(df))], function(x) df[[x]])))
    global_range[1] <- global_range[1]-1 
    global_range[2] <- global_range[2]+1

    d <- plotly::highlight_key(df, ~sample)
    base <- plotly::plot_ly(
        d, 
        text = ~sample,
        # hoverinfo = "text",
        type = "scatter",
        mode = "markers",
        color = ~project,
        colors = "Set1",
        marker = list(size = 10),
        showlegend = FALSE
    )
    fig <- plotly::subplot(
      plotly::add_markers(base, x = ~global_x_shift, y = ~sitk_global_x_shift,
        hovertemplate = paste0('<b>%{text}</b><br>X error Landmarks: %{y:.2f}<br>X error sitk: %{x:.2f}')) |>
        plotly::layout(
        xaxis = list(range=global_range, title = "X translation"),
        yaxis = list(range=global_range, title = "X translation sitk")
      ),
      plotly::add_markers(base, x = ~global_y_shift, y = ~sitk_global_y_shift,
        hovertemplate = paste0('<b>%{text}</b><br>Y error Landmarks: %{y:.2f}<br>Y error sitk: %{x:.2f}')) |>
        plotly::layout(
        xaxis = list(range=global_range, title = "Y translation"),
        yaxis = list(range=global_range, title = "Y translation sitk")
      ),
      plotly::add_markers(base, x = ~global_shift, y = ~sitk_global_shift,
        hovertemplate = paste0('<b>%{text}</b><br>Error Landmarks: %{y:.2f}<br>Error sitk: %{x:.2f}')) |>
        plotly::layout(
        xaxis = list(title = "translation"),
        yaxis = list(title = "translation sitk")
      )
    ) |> 
      plotly::add_annotations(
        text = "X translation",
        x = 0.15,
        y = 1,
        yref = "paper",
        xref = "paper",
        yanchor = "bottom",
        showarrow = FALSE,
        font = list(size = 15)
      ) |> 
      plotly::add_annotations(
        text = "Y translation",
        x = 0.5,
        y = 1,
        yref = "paper",
        xref = "paper",
        yanchor = "bottom",
        showarrow = FALSE,
        font = list(size = 15)
      ) |> 
      plotly::add_annotations(
        text = "Error",
        x = 0.85,
        y = 1,
        yref = "paper",
        xref = "paper",
        yanchor = "bottom",
        showarrow = FALSE,
        font = list(size = 15)
      ) |>
        plotly::layout(
        xaxis = list(title = "Landmarks"),
        yaxis = list(title = "sitk"),
        margin = list(t=50, b=150, l=50, r=50)
      ) |>
      plotly::highlight(on = "plotly_hover", off = "plotly_doubleclick")
    fig
}
```


```{r}
dice_distance_plot <- function(input_csv_files, vis_type){
    df <- read.csv(input_csv_files)
    vis_type_ls <- strsplit(vis_type,"_to_")[[1]]


    library(ggplot2)
    df$dice_score <- df[[colnames(df)[grepl(sprintf("dice_score_%s_%s",vis_type_ls[1],vis_type_ls[2]),colnames(df))]]]
    df$centroid_distances <- df[[colnames(df)[grepl(sprintf("euclidean_distance_centroids_%s",vis_type),colnames(df))]]]

    ggplot(df, aes(dice_score, centroid_distances)) +
     geom_point() +
     theme_minimal()
}
```



# IMS to postIMS

## Ablation marks & registered IMS pixels {.tabset}

| Color | Description  |
|-------|--------------|
| Blue  | Ablation marks |
| Green | IMS pixel    |

```{r, results='asis', fig.width=8, fig.height=8}
cat("\n\n")
for (i in seq_along(IMS_to_postIMS_svg)) {
    filename <- IMS_to_postIMS_svg[i]
    if(file.exists(filename)){
        cat(sprintf("\n\n### %s\n\n",sample_names[i]))
        cat(sprintf("![](%s)",filename))
    }
}
cat("\n\n")
```


## Distances ablation marks to IMS pixels

```{r, fig.width=8, fig.height=8}
create_error_plot(input_csv_files, "IMS_to_postIMS")
```


# preIMS to postIMS

## preIMS image registered to postIMS images
Global images or images per core

## Tissue masks {.tabset}

| Color | Description |
|-------|-------------|
| Black | Neither     |
| White | Both        |
| Gray  | One of the two |


```{r, results='asis', fig.width=8, fig.height=8}
cat("\n\n")
for (i in seq_along(preIMSmask_to_postIMSmask_png)) {
    filename <- preIMSmask_to_postIMSmask_png[i]
    if(file.exists(filename)){
        cat(sprintf("\n\n### %s\n\n",sample_names[i]))
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" width=\"1000\"/>",filename))
        # cat(sprintf("![](%s)",filename))
    }
}
cat("\n\n")
```


## Distances between centroids of masks

```{r, fig.width=8, fig.height=8}
plotly::ggplotly(dice_distance_plot(input_csv_files, "preIMS_to_postIMS"))
```

## Images of Landmarks {.tabset}

```{r, results='asis', fig.width=8, fig.height=8}
cat("\n\n")
for (i in seq_along(landmarks_preIMS_transformed_on_postIMS_png)) {
    filename1 <- landmarks_preIMS_transformed_on_postIMS_png[i]
    filename2 <- landmarks_postIMS_png[i]
    if(file.exists(filename1) & file.exists(filename2)){
        cat(sprintf("\n\n### %s\n\n",sample_names[i]))
        cat("<p float=\"left\">")
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" width=\"50%%\"/>",filename1))
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" width=\"50%%\"/>",filename2))
        cat("</p>")
    }
}
cat("\n\n")
```


## Distances between Landmarks

```{r, fig.width=8, fig.height=8}
create_error_plot(input_csv_files, "preIMS_to_postIMS")
```


## Translations based on grid subtracted postIMS to preIMS registration

```{r, fig.width=10, fig.height=5}
fig <- sitk_error_plot(input_csv_files, "preIMS_to_postIMS")
fig
```


# preIMC to preIMS

## preIMC images registered to preIMS images
Global or per region

## Tissue masks {.tabset}

| Color | Description |
|-------|-------------|
| Black | Neither     |
| White | Both        |
| Gray  | One of the two |


```{r, results='asis', fig.width=8, fig.height=8}
cat("\n\n")
for (i in seq_along(preIMCmask_to_preIMSmask_png)) {
    filename <- preIMCmask_to_preIMSmask_png[i]
    if(file.exists(filename)){
        cat(sprintf("\n\n### %s\n\n",sample_names[i]))
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" width=\"1000\"/>",filename))
        # cat(sprintf("![](%s)",filename))
    }
}
cat("\n\n")
```


## Distances between centroids of masks

```{r, fig.width=8, fig.height=8}
dice_distance_plot(input_csv_files, "preIMC_to_preIMS")
```


## Images of Landmarks {.tabset}

```{r, results='asis', fig.width=8, fig.height=8}
cat("\n\n")
for (i in seq_along(landmarks_preIMC_transformed_on_preIMS_png)) {
    filename1 <- landmarks_preIMC_transformed_on_preIMS_png[i]
    filename2 <- landmarks_preIMS_png[i]
    if(file.exists(filename1) & file.exists(filename2)){
        cat(sprintf("\n\n### %s\n\n",sample_names[i]))
        cat("<p float=\"left\">")
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" width=\"50%%\"/>",filename1))
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" width=\"50%%\"/>",filename2))
        cat("</p>")
    }
}
cat("\n\n")
```


## Distances between Landmarks

```{r, fig.width=8, fig.height=8}
create_error_plot(input_csv_files, "preIMC_to_preIMS")
```


## Distances between MSER's




# postIMC to preIMC

## postIMC images registered to preIMC images
Global

## Tissue masks {.tabset}

| Color | Description |
|-------|-------------|
| Black | Neither     |
| White | Both        |
| Gray  | One of the two |


```{r, results='asis', fig.width=8, fig.height=8}
cat("\n\n")
for (i in seq_along(postIMCmask_to_preIMCmask_png)) {
    filename <- postIMCmask_to_preIMCmask_png[i]
    if(file.exists(filename)){
        cat(sprintf("\n\n### %s\n\n",sample_names[i]))
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" width=\"1000\"/>",filename))
        # cat(sprintf("![](%s)",filename))
    }
}
cat("\n\n")
```


## Distances between centroids of masks

```{r, fig.width=8, fig.height=8}
dice_distance_plot(input_csv_files, "postIMC_to_preIMC")
```

## Images of Landmarks {.tabset}

```{r, results='asis', fig.width=8, fig.height=8}
cat("\n\n")
for (i in seq_along(landmarks_postIMC_transformed_on_preIMC_png)) {
    filename1 <- landmarks_postIMC_transformed_on_preIMC_png[i]
    filename2 <- landmarks_preIMC_png[i]
    if(file.exists(filename1) & file.exists(filename2)){
        cat(sprintf("\n\n### %s\n\n",sample_names[i]))
        cat("<p float=\"left\">")
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" width=\"50%%\"/>",filename1))
        cat(sprintf("<img src=\"%s\" alt=\"drawing\" width=\"50%%\"/>",filename2))
        cat("</p>")
    }
}
cat("\n\n")
```



## Distances between Landmarks

```{r, fig.width=8, fig.height=8}
create_error_plot(input_csv_files, "postIMC_to_preIMC")
```


